\documentclass{article}
\author{MBAEKWE UGOCHI}
\begin{document}
	\section{PROGRAMMING LANGUAGES}
	There are five programming languages that I am going to be discussing: 
	\begin{enumerate}
		\item PYTHON
		\item SWIFT
		\item C++
		\item GOLANG
		\item JAVA
	\end{enumerate}
\section{PYTHON}
\subsection{HISTORY OF PYTHON}
Python was developed in the late periods of 1980 by a man called Guido van Rossum  at Centrum Wiskunde.
\subsubsection{Where can python be applied?}
Python is mostly adopted for machine learning and artificial intelligence it can be applied in:
\begin{itemize}
	\item Data Analytics
	\item Web development
	\item Game development
	\item Designs
\end{itemize}
	Some companies like Instagram,Spotify and Amazon make use of python as their programming language. 
	\subsubsection{Python INTEGRATED DEVELOPMENT ENVIRONMENT}
	\begin{itemize}
		\item Spyder
		\item PYCHARM
		\item THONNY
		\item ATOM
		\item JUPYTER NOTEBOOK
	\end{itemize}	
\section{SWIFT}
\subsection{HISTORY OF SWIFT}
Swift was developed in 2010 by Chris Lattner it is sometimes said to have been a replacement of Objective C.
\subsection{Where can it be applied?}
\begin{itemize}
	\item Swift is a general open source programming language developed by apple which means that it is used and applied in the development of ios and Mac OS.
	\item Swift is used by companies like Apple and Slack.
\end{itemize}
\subsection{SWIFT INTEGRATED DEVELOPMENT ENVIRONMENT(IDE)}
\begin{itemize}
	\item Apple developer
	\item App code
	\item Xcode
	\item C lion
	\end{itemize}
	\section{JAVA}
	\subsection{HISTORY OF JAVA}
	Java was invented by James Gosling in 1995 at sun microsystem.
	\subsection{Where can it be applied?}
	\begin{itemize}
		\item Business Application
		\item Cloud-Based Application
		\item Big Data Technologies
		\item Scientific Applications
		\item Game Applications
		\item Companies like ibm, hcl and Infosys
	\end{itemize}
\subsection{JAVA INTEGRATED DEVEOPMENT ENVIRONMENT (IDE)}
\begin{itemize}
	\item Jgrasp
	\item DrJava
	\item NetBeans
	\item JDeveloper
\end{itemize}
\section{GOLANG}
\subsection{HISTORY OF GOLANG}
It was developed by Google in year 2007 for apis and web applications.
\subsection{Where can it be applied?}
\begin{itemize}
\item News Outlets
\item Media Platform
\item Distributed Network Services
 Companies that use golang are
GOOGLE, UBERAD twitch
\end{itemize}
\section{C++}
\subsection{HISTORY OF C++}
C++ was ceated by Bjarne Stroustrup in 1979it was formally known as C with Object, up until 1983
\subsubsection{WHERE CAN IT BE APPLIED?}
\begin{itemize}
	\item GAME DEVELOPMENT
	\item BANKING APPLICATIONS
	\item DATABASE SOFTWARE
\end{itemize}
 \subsubsection{C++ INTEGRATED DEVELOPMENT (IDE)C++ INTEGRATED DEVELOPMENT (IDE)}
\begin{itemize}
	\item DEV-C++
	\item QT CREATOR
	\item CODELITE
\end{itemize}

	
	

		


\end{document}
